\documentclass[letterpaper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern} % Use modern fonts
\usepackage{enumitem} % Customize bullet points
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{tabto}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{setspace}
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

\urlstyle{same}
\pagestyle{fancy}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
	\vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
	\onehalfspacing
	\textbf{\LARGE Vishnuvrithan R T} \\ \vspace{1pt}
	
	\begin{center}
		\begin{multicols}{2}
			\begin{flushleft}
				\href{{https://github.com/vishnuvrithan/}}{GitHub}\\
				\href{{https://www.linkedin.com/in/vishnuvrithan-r-352a37193/}}{LinkedIn}
			\end{flushleft}
			
			\begin{flushright}
				m: (+91)9747481104\\
				e: \url{vishnuvrithanravi123@gmail.com}
			\end{flushright}
		\end{multicols}
	\end{center}
	
	\underline{\large Career Objective:}
	\newline
	Dynamic and results-driven software engineer with 3.5 years of experience in API and kernel development at Infosys, complemented by contract roles with Cisco and Netflix. Adept at leveraging cutting-edge technologies to drive performance improvements and deliver innovative solutions. Passionate about tackling complex challenges and contributing to the success of forward-thinking teams. Seeking a challenging role that allows me to utilize my technical expertise, problem-solving skills, and enthusiasm for technology to drive impactful results and foster professional growth.
	
	\underline{\large Education:}
	\begin{itemize}
		\item \textbf{B Tech}\\
		Govt. Rajiv Gandhi Institute of Technology (June 2016 - October 2020), Electronics and Communication Engineering, Kottayam\tab Kerala Technological University (KTU).\\
		\item \textbf{Plus Two}\\
		St. Joseph's HSS (2014 - 2015), Science, Anjengo \tab Kerala Board.\\
		\item \textbf{SSLC}\\
		SSPB Higher Secondary School (2013), Kadakkavoor \tab Kerala Board.
	\end{itemize}
	
	%-----------EXPERIENCE-----------
	\underline{\large Experience:}
	\begin{itemize}
		\item \textbf{Infosys} \hfill \textit{June 2021 - August 2024}
		\begin{itemize}
			\item Spearheaded both API and kernel development projects, contributing to the enhancement of system functionalities and performance.
			\item Developed robust APIs to support scalable applications, improving integration and data exchange capabilities.
			\item Implemented kernel-level modifications to optimize system performance and address critical issues.
			\item Collaborated with cross-functional teams to deliver high-impact solutions and ensure alignment with project goals.
		\end{itemize}
		
		\item \textbf{Cisco (Contract)} \hfill \textit{June 2022 - December 2022}
		\begin{itemize}
			\item Worked as a contract employee on network security and performance optimization projects, contributing to enhancing network reliability.
		\end{itemize}
		
		\item \textbf{Netflix (Contract)} \hfill \textit{January 2023 - June 2023}
		\begin{itemize}
			\item Engaged in developing streaming technologies and API integrations, supporting high-quality video delivery and user experience.
		\end{itemize}
	\end{itemize}
	
	%-----------CORE COMPETENCIES-----------
	\underline{\large Core Competencies:}\setstretch{1.5}
	\newline
	Java, Python3, C, C++, MongoDB, Mulesoft, Arduino Uno, Wireshark, cmd, Bash, PowerShell, Matlab, Shell Scripting, Video Production, Linux/Unix Administration, VMWare.
	
	%-----------CERTIFICATIONS-----------
	\underline{\large Certifications:}
	\begin{itemize}
		\item Java
		\item Spring Framework
		\item Spring Boot
		\item MongoDB
		\item Proficient in Anypoint Studio
		\item UiPath Automation (2 years of experience)
	\end{itemize}
	
	%-----------PERSONAL PROJECTS-----------
	\underline{\large Personal Projects:}\setstretch{1.5}
	\newline
	\textbf{Smart Concession Card (SMC).}\\
	SMC offers a comprehensive system for managing tickets issued to students in public transport networks and an automated fare collection and detection system. It replaces traditional manual fare collection methods with an automated approach, facilitating faster transactions, reducing operational costs, and enhancing payment efficiency.
	
	%-----------INTERNSHIPS AND WORKSHOPS-----------
	\underline{\large Internships and Workshops:}
	\begin{itemize}
		\item \textbf{Internship-1:} Keltron - Power Electronics Group (PEG), Transformer Winding, Electroplating, Security and Surveillance Group (SSG), Intelligent Tracking and Communication Technology Development Centre.\\
		\item \textbf{Internship-2:} Introduction to Web Development and Technology (basics of HTML, CSS, Apache2).\\
		\item \textbf{Internship-3:} Neo Green Lab – Raspberry Pi, Python3.\\
		\item \textbf{Workshops:} Introduction to Robotics at MAC College, ISTE Workshop at Kannur (line follower, introduction to Arduino), 3D Printing Technology (Basics).
	\end{itemize}
	
	%-----------HOBBIES-----------
	\underline{\large Hobbies:}
	\begin{itemize}
		\item Playing Badminton, Swimming, Chess, Gardening
		\item Data Encryption and Decryption
		\item Exploring advancements in emerging technologies, reviewing movies and books
	\end{itemize}
	
	%-----------LANGUAGES KNOWN-----------
	\underline{\large Languages Known:}
	\begin{itemize}
		\item Fluent in Malayalam and English.
		\item Proficient in understanding Tamil, Hindi, and Telugu.
	\end{itemize}
	
	%-----------PERSONAL DETAILS-----------
	\underline{\large Personal Details:}\\
	\begin{itemize}
		\item Name: Vishnuvrithan R T
		\item Address: Thodiyilveedu, Vakkom PO, Vakkom, Pin 695308, Thiruvananthapuram
		\item DOB: 28/04/1997
	\end{itemize}
	
\end{document}
